---
title: Tidy Tuesday 52 2020
author: Andreas Kitsche
date: '2021-01-07'
slug: tidy-tuesday-52-2020
categories:
  - R
  - tidytuesday
tags:
  - rmarkdown
  - tidytuesday
subtitle: ''
summary: ''
authors: []
lastmod: '2021-01-07T13:29:02+01:00'
featured: no
image:
  caption: ''
  focal_point: ''
  preview_only: no
projects: []
bibliography: ["references.bib", "references_auto.bib"]
---


```{r include = FALSE}
library(xaringanExtra)
# enable panelset
use_panelset()
# style_panelset_tabs(foreground = "honeydew", background = "seagreen")
```


```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE)
if (!require("pacman")) install.packages("pacman")
```


```{r packages, include=FALSE}
pacman::p_load(c("reticulate", "bookdown", "knitr", "tidyverse"))
```

```{r bib, include=FALSE}
knitr::write_bib(c("reticulate", "bookdown"), "references_auto.bib")
```


Hey folks,

this is the first of a series of blog post where I want to participate on the [tidytuesday](https://github.com/rfordatascience/tidytuesday/blob/master/README.md) weekly social data project in R. 

> The intent of Tidy Tuesday is to provide a safe and supportive forum for individuals to practice their wrangling and data visualization skills independent of drawing conclusions.

The goal of this series is to help me


* practice data visualization and data wrangling in R (@R-base) using the tidyverse (@tidyverse)
* adopt this skillset to learn Python
* master to publish the applications using [R Markdown](https://bookdown.org/yihui/rmarkdown-cookbook/)

::::: {.panelset}

<!-- First panel -->
::: {.panel}
[R code]{.panel-name}

Check the R code below:
```{r echo = TRUE, eval = FALSE}
lm(mpg ~ drat, data = mtcars)
```
:::

<!-- Second panel -->
::: {.panel}
[Stata code]{.panel-name}

```
regress y x

```
:::

<!-- Third panel -->
::: {.panel}
[R output]{.panel-name}
```{r echo = FALSE, eval = TRUE}
lm(mpg ~ drat, data = mtcars)
```
:::

::::

# References
